Eco Tracker Appendix

### 2025-03-18 paper/appendix.tex
Fix typos in appendinx

There were two optimizatiosn performed to tune the agent.
The first optimization involved the hyper paper tuning of alpha, gamma, epsilon, epsilon decay, $n\_steps$, episode count with rewards of 1.0 per send message and \-1.5 per lost message and 0.0001 of power multiplier.
The second optimization was a reward shaping optimization and tuned rewards for performing each action, the power multiplier, and the reward for sending a message.

@@

The reward shaping optimization resulted in an agent with a maximum message count of 253.
The agent was able to learn a long-term strategy and was able to balance short-term rewards with long-term goals.
The agent appears to need intermediate rewards to learn a long-term strategy.
The followin parameters were found: power reward =0.000, Action0=-1.17324902,Action1=-0.463915495, Action2=-2, PerMessage=	0.602358605

>>>>

There were two optimizatiosn performed to tune the agent.
The first optimization involved the hyperparameter tuning of alpha, gamma, epsilon, epsilon decay, $n\_steps$, episode count with rewards of 1.0 per send message and \-1.5 per lost message and 0.0001 of power multiplier.
The second optimization was a reward shaping optimization and tuned rewards for performing each action, the power multiplier, and the reward for sending a message.

@@

The reward shaping optimization resulted in an agent with a maximum message count of 253.
The agent was able to learn a long-term strategy and was able to balance short-term rewards with long-term goals.
The agent appears to need intermediate rewards to learn a long-term strategy.
The following parameters were found: power reward =0.000, Action0=-1.17324902,Action1=-0.463915495, Action2=-2, PerMessage=	0.602358605

It is interesting that the reward shaping produced a better result than pure message count.
The reward shaping shows the agent which actions should be rewarded to produce a better message count.
This is likely because the gradient of rewards did not provide enough information to the agent to learn a long-term strategy for the hyper parameter tuning case.
